Quantum Interval-Valued Probability: Contextuality and the Born Rule

### 2017-08-14 prop_letter.tex
before merge

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\mathrm{C}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality\nb\cite{BarrettKent2004,Appleby_2005}, which refers
to the fact that the results of measuring compatible sets of
observables depend on whether they are measured together or
separately.  For example, Meyer\nb\cite{PhysRevLett.83.3751} and
Mermin\nb\cite{Mermin1999} disagree on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem\nb\cite{kochenspecker1967,peres1995quantum}, which is a
mathematical statement about contextuality.  The Kochen-Specker
theorem asserts that, in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator\nb$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that one {\it can\/}
assign definite values $0$ or $1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem\nb\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration. Mermin therefore claimed that the
impact of Meyer's negative result is
``unsupportable''\nb\citep{Mermin1999}.  Discussion has continued on
whether contextuality is consistent with experimental
outcomes\nb\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
A fundamental question is how to address this controversy by
developing mathematical theories of quantum mechanics that are
intrinsically, rather than only implicitly, consistent with the
resources available for the realistic accuracy of an actual
measurement.

In this paper, we extend our previous work on the foundations of
computability in quantum physics by exploring the application of
interval-valued probability measures (IVPM) to achieving a coherent
formulation of finite-resource quantum mechanics.  To this end, we
develop a mathematical framework that includes the uncertainties of
finite precision and imperfections in the quantum measurement
process. In particular, we quantify the concept of imperfect quantum
measurement and its impact on the interpretation of the Kochen-Specker
and Gleason theorems and their implications for the foundations of
quantum mechanics.  Our first observation is that essential objectives
of our program to achieve a computable theory of quantum mechanics and
finite-resource measurement, attempted previously with computable
number systems\nb\cite{usat,geometry2013apsrev4,DQT2014}, may be
achievable by extending classical interval-valued probability
measures\nb\cite{JamisonLodwick2004} to the quantum domain.  We thus
begin by axiomatizing a quantum interval-valued probability measure
(QIVPM) framework.

The effect of finite precision and imperfections on contextuality and
the Kochen-Specker theorem is shown to have a resolution in terms of
our QIVPM framework.  To proceed, we use a formulation of the
``Mermin-Peres square''\nb\cite{peres1995quantum,Mermin1990Simple}
that uses the expectation value of a physical observable with respect
to a QIVPM, where the interval-valued expectation value is consistent
with the expectation value of the same observable in conventional
quantum mechanics with infinite resources. We show that, as long as
errors and uncertainties remain smaller than a particular value, the
Kochen-Specker theorem remains valid. In other words, we established a
rigorous bound for its validity and, therefore, the limits for
physical reality to remain contextual.

A key aspect of a quantum measurement is its statistical nature, as
reflected by application of the Born rule to determine the probability
of a given measurement
outcome\nb\citep{Born1983,peres1995quantum,544199}. The Gleason
theorem establishes that there is no alternative to the Born rule by
demonstrating, using reasonable continuity arguments in Hilbert spaces
of dimension $d\ge3$, the existence of a unique state $\rho$
consistent with the statistical predictions computed from that
rule\nb\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  It is
then legitimate to question what happens when infinite precision
cannot be achieved. We will show that, if the effect of finite
precision is incorporated, while a QIVPM might not be consistent with
a unique state\nb$\rho$ on all projectors defined on a Hilbert space
of dimension $d\ge3$, there is a mathematically precise sense in which
one recovers the original Gleason theorem asymptotically.
Specifically, if for bounded resources the QIVPM is induced by some
states\nb$\rho'$, those states will converge to a unique state $\rho$
when the size of the intervals characterizing the uncertainties tends
to zero.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events\nb\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In
the quantum case, the events of interest are specified by
\emph{projection operators} $P$. These include the empty
projection\nb$\mathbb{0}$, the identity projection\nb$\mathbb{1}$,
projections of the form $\proj{\phi}$ where $\ket{\phi}$ is a pure
quantum state (an element of a Hilbert space), sums of
\emph{orthogonal} projections $P_0$ and $P_1$ with
$P_0P_1=\mathbb{0}$, and products of \emph{commuting} projections
$P_0$ and $P_1$ with $P_0P_1=P_1P_0$. In a well-defined quantum
probability
space\nb\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped to a probability\nb$\mu(P_{i})$ using a
probability measure\nb$\mu:\events\rightarrow[0,1]$, where $\events$
is the set of all projections on a given Hilbert space, subject to the
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projections $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}\nb$[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. The collection of intervals used in the
definition of a probability measure must satisfy certain properties
that we explain next.

@@

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the previous naïve way of combining the intervals would
give $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
probability interval. Moreover the event $E\cup\overline{E}$ is the
identity event covering the entire space; its probability interval
should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
that the two intervals are correlated: there is more information in
the combined event than in each event separately. In our example, even
though the true probability of $\mu(E)$ can be anywhere in the range
$[0.2,0.3]$ and the true probability of $\mu(\overline{E})$ can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the identity event would force
$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
particular assignments of $\mu(E)$ or $\mu(\overline{E})$.

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM\nb$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator\nb$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projections $P_0$
  and $P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
\noindent The first three constraints, Eqs.\nb(\ref{eq:QIVPM-constraints}), are
the direct counterpart of the corresponding ones for IVPMs.  With the
understanding that the union of classical sets $E_1\cup E_2$ is
replaced by $P_0+P_1-P_0P_1$ in the case of quantum projection
operators~\cite{Griffiths2003}, the last condition,
Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}), is a
direct counterpart of Eq.~(\ref{eq:classicalconvex}).

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with the
measure\nb$\bar{\mu}$ acting on a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\citep{Born1983,peres1995quantum,544199}. Given a set
of projectors\nb$S$, 
\begin{equation}
\coreBorn\left(\bar{\mu},S\right)=\set{\textrm{state }\rho}{\forall P\in S\ \mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}
\end{equation}
is the set of all states consistent with $\bar{\mu}$ on every
projector in $S$. For example, assuming the three intervals $\imposs$,
$\necess$, and $\unknown=\left[0,1\right]$, then:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\unknown\,, & \text{otherwise,}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
is a QIVPM. This measure represents the beliefs of an experimenter
with no prior knowledge about the particular quantum system in
question; any quantum state would be consistent with $\bar{\mu}_{1}$
on any projectors, and $\coreBorn\left(\bar{\mu}_{1},\events\right)$
is just the set of all states.

As mentioned earlier, QIVPMs become classical IVPMs when the space of
events includes only mutually commuting events. We define
$\events'\subseteq\events$ to be a sub-event space if it satisfies the
following conditions.
\begin{itemize}
\item $\left\{ \mathbb{0},\mathbb{1}\right\} \subseteq\events'$.
\item For any projection\nb$P\in\events'$, we have $\mathbb{1}-P\in\events'$. 
\item For each pair of orthogonal projections\nb$P_0 \in \events'$ and
  $P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. 
\end{itemize}

For example, $\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a commuting sub-event space. Consider $\bar{\mu}_{1}$ defined
in the previous paragraph. Restricting $\bar{\mu}_{1}$ to
$\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\,.
\end{equation}
If we identify the states \nb$\proj{0}$ and $\proj{1}$ with the head
and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
the situation in which that an experimenter knows nothing about a coin
before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
state\nb$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability\nb$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with
$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin should be
consistent with the situation for which an experimenter has no prior
knowledge.

@@

Our first result is that a QIVPM is consistent with the inability to avoid
uncertainty found in conventional infinite precise quantum
mechanics\nb\cite{PeresRon1988,peres1995quantum}.

>>>>

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{framed}
\newcommand{\amr}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{green}{Amr says: #1}\end{minipage}\end{framed}}
\newcommand{\yutsung}[1]{\begin{framed}\begin{minipage}{0.9\linewidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}\end{framed}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\newcommand{\Tr}{\ensuremath{\mathop{\mathrm{Tr}}\nolimits}}
\allowdisplaybreaks
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
\setcounter{secnumdepth}{3}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[1] }

@@

There are long-standing debates in the foundations of quantum
mechanics regarding the tension between finite precision measurement
and contextuality~\cite{BarrettKent2004,Appleby_2005}, which refers
to the fact that the results of measuring compatible sets of
observables depend on whether they are measured together or
separately.  For example, Meyer~\cite{PhysRevLett.83.3751} and
Mermin~\cite{Mermin1999} disagree on whether finite-precision
measurements invalidate the spirit of the Kochen-Specker
theorem~\cite{kochenspecker1967,peres1995quantum}, which is a
mathematical statement about contextuality.  The Kochen-Specker
theorem asserts that, in a Hilbert space of dimension $d \ge 3$, it is
impossible to associate definite measured values, $\mu(P_i)= 0$ or
$1$, with every projection operator~$P_i$, in such a way that, if a
set of commuting $P_i$ satisfies $\sum_i P_i = 1$, then
$\sum_i \mu(P_i) = 1$. In contrast, Meyer showed that one {\it can\/}
assign definite values $0$ or $1$ to the measurement outcome
$\mu(P_i)$ when the Hilbert space is defined over the field of
rational numbers, therefore nullifying the
theorem~\citep{PhysRevLett.83.3751}.  However, Mermin then argued
that measurement outcomes must depend smoothly on slight changes in
the experimental configuration. Mermin therefore claimed that the
impact of Meyer's negative result is
``unsupportable''~\citep{Mermin1999}.  Discussion has continued on
whether contextuality is consistent with experimental
outcomes~\citep{Kent1999,HavlicekKrennSummhammerSvozil2001,SimonBruknerZeilinger2001,Cabello2002,Larsson2002,Appleby2002,Peres2003,BarrettKent2004,Appleby_2005,Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.
A fundamental question is how to address this controversy by
developing mathematical theories of quantum mechanics that are
intrinsically, rather than only implicitly, consistent with the
resources available for the realistic accuracy of an actual
measurement.

In this paper, we extend our previous work on the foundations of
computability in quantum physics by exploring the application of
interval-valued probability measures (IVPM) to achieving a coherent
formulation of finite-resource quantum mechanics.  To this end, we
develop a mathematical framework that includes the uncertainties of
finite precision and imperfections in the quantum measurement
process. In particular, we quantify the concept of imperfect quantum
measurement and its impact on the interpretation of the Kochen-Specker
and Gleason theorems and their implications for the foundations of
quantum mechanics.  Our first observation is that essential objectives
of our program to achieve a computable theory of quantum mechanics and
finite-resource measurement, attempted previously with computable
number systems~\cite{usat,geometry2013apsrev4,DQT2014}, may be
achievable by extending classical interval-valued probability
measures~\cite{JamisonLodwick2004} to the quantum domain.  We thus
begin by axiomatizing a quantum interval-valued probability measure
(QIVPM) framework.

The effect of finite precision and imperfections on contextuality and
the Kochen-Specker theorem is shown to have a resolution in terms of
our QIVPM framework.  To proceed, we use a formulation of the
``Mermin-Peres square''~\cite{peres1995quantum,Mermin1990Simple}
that uses the expectation value of a physical observable with respect
to a QIVPM, where the interval-valued expectation value is consistent
with the expectation value of the same observable in conventional
quantum mechanics with infinite resources. We show that, as long as
errors and uncertainties remain smaller than a particular value, the
Kochen-Specker theorem remains valid. In other words, we established a
rigorous bound for its validity and, therefore, the limits for
physical reality to remain contextual.

A key aspect of a quantum measurement is its statistical nature, as
reflected by application of the Born rule to determine the probability
of a given measurement
outcome~\citep{Born1983,peres1995quantum,544199}. The Gleason
theorem establishes that there is no alternative to the Born rule by
demonstrating, using reasonable continuity arguments in Hilbert spaces
of dimension $d\ge3$, the existence of a unique state $\rho$
consistent with the statistical predictions computed from that
rule~\citep{gleason1957,Redhead1987-REDINA,peres1995quantum}.  It is
then legitimate to question what happens when infinite precision
cannot be achieved. We will show that, if the effect of finite
precision is incorporated, while a QIVPM might not be consistent with
a unique state~$\rho$ on all projectors defined on a Hilbert space
of dimension $d\ge3$, there is a mathematically precise sense in which
one recovers the original Gleason theorem asymptotically.
Specifically, if for bounded resources the QIVPM is induced by some
states~$\rho'$, those states will converge to a unique state $\rho$
when the size of the intervals characterizing the uncertainties tends
to zero.

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections of
uncertain
events~\cite{Kolmogorov1950,544199,Griffiths2003,Grabisch2016}. In the
quantum case, the events of interest are specified by \emph{projection
  operators} $P$. These include the empty projector~$\mathbb{0}$,
the identity projector~$\mathbb{1}$, projectors of the form
$\proj{\phi}$ where $\ket{\phi}$ is a pure quantum state (an element
of a Hilbert space), sums of \emph{orthogonal} projectors $P_0$
and~$P_1$ with $P_0P_1=\mathbb{0}$, and products of \emph{commuting}
projectors $P_0$ and~$P_1$ with $P_0P_1=P_1P_0$. In a well-defined
quantum probability
space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is mapped to a probability~$\mu(P_{i})$ using a
probability measure~$\mu:\events\rightarrow[0,1]$, where $\events$
is the set of all projectors on a given Hilbert space, subject to the
following constraints: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each pair
of \emph{orthogonal} projectors $P_{0}$ and $P_{1}$:
\begin{equation}
{\mu}\left(P_{0}+P_{1}\right)={\mu}\left(P_{0}\right)+{\mu}\left(P_{1}\right)\,.\label{eq:QuantumProbability-Addition}
\end{equation}

@@

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single \emph{real number} to an \emph{interval}~$[\ell,r]$
where~$\ell$ intuitively corresponds to the strength of evidence for
the event~$E$ and~$1-r$ corresponds to the strength of evidence
against the same event. The collection of intervals used in the
definition of a probability measure must satisfy certain properties
that we explain next.

@@

Let $E_1$ and $E_2$ be two disjoint events with probabilities
$\mu(E_1)=[\ell_1,r_1]$ and $\mu(E_2)=[\ell_2,r_2]$. A first attempt
at calculating the probability of the combined event that
\emph{either} $E_1$ or $E_2$ occurs might be
$\mu(E_1\cup E_2) = [\ell_1+\ell_2,r_1+r_2]$. In some cases, this is
indeed a sensible definition. For example, if $\mu(E_1)=[0.1,0.2]$ and
$\mu(E_2)=[0.3,0.4]$ we get $\mu(E_1\cup E_2) = [0.4,0.6]$. But
consider an event $E$ such that $\mu(E)=[0.2,0.3]$ and hence
$\mu(\overline{E})=[0.7,0.8]$. The two events $E$ and $\overline{E}$
are disjoint; the previous naïve way of combining the intervals would
give $\mu(E\cup\overline{E})=[0.9,1.1]$ which is not a valid
probability interval. Moreover the event $E\cup\overline{E}$ is the
identity event covering the entire space; its probability interval
should be $[1,1]$ which is sharper than $[0.9,1.1]$. The problem is
that the two intervals are correlated: there is more information in
the combined event than in each event separately. In our example, even
though the true probability of $\mu(E)$ can be anywhere in the range
$[0.2,0.3]$ and the true probability of $\mu(\overline{E})$ can be in
anywhere in the range $[0.7,0.8]$, the values are not independent. Any
value of $\mu(E) \leq 0.25$ will force $\mu(\overline{E})\geq
0.75$. To account for such subtleties, the axioms of interval-valued
probability do not use a strict equality for the combination of
disjoint events. The correct constraint regarding the probability of
$E_1\cup E_2$ when $E_1$ and $E_2$ are disjoint is
$\mu(E_1\cup E_2) \subseteq [\ell_1+\ell_2,r_1+r_2]$ which, in
combination with the requirement for the identity event would force
$\mu(E \cup \overline{E})$ to always be $[1,1]$ irrespective of the
particular assignments of $\mu(E)$ or~$\mu(\overline{E})$.

When combining non-disjoint events, there is a further subtlety whose
resolution will give us the final general condition for IVPMs. For
general, not necessarily disjoint, events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}~\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

\begin{definition}[QIVPM]
  Assume a collection of intervals $\mathscr{I}$ including
  $\imposs=[0,0]$ and $\necess=[1,1]$ with addition and scalar
  multiplication defined as follows:
  \begin{subequations}\label{eq:interval-operations}
  \begin{eqnarray}
   &  & [\ell_{1},r_{1}]+[\ell_{2},r_{2}]=[\ell_{1}+\ell_{2},r_{1}+r_{2}]\textrm{ and}\\
   &  & x[\ell,r]=\begin{cases}
  [x\ell,xr] & \textrm{for }x\ge0\,;\\{}
  [xr,x\ell] & \textrm{for }x\le0\,.
  \end{cases}
  \end{eqnarray}
  \end{subequations}
  Then we take a QIVPM~$\bar{\mu}$ to be an assignment of an interval to each
  event (projection operator~$P$) subject to the following constraints:
  \begin{subequations}\label{eq:QIVPM-constraints}
  \begin{eqnarray}
   &  & \bar{\mu}(\mathbb{0})=\left[0,0\right]\,,\\
   &  & \bar{\mu}(\mathbb{1})=\left[1,1\right]\,,\\
   &  & \bar{\mu}\left(\mathbb{1}-P\right)=\left[1,1\right]-\bar{\mu}\left(P\right)\,,
  \end{eqnarray}
  \end{subequations}
  and satisfying for each pair of \emph{commuting} projectors $P_0$
  and $P_1$ with $P_0P_1=P_1P_0$,
\begin{equation}
\bar{\mu}\left(P_{0}+P_{1}-P_{0}P_{1}\right)+\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\,.
\label{eq:QuantumInterval-valuedProbability-Inclusion}
\end{equation}
\end{definition}
\noindent The first three constraints,
Eqs.~(\ref{eq:QIVPM-constraints}), are the direct counterpart of the
corresponding ones for classical IVPMs.  With the understanding that the union
of classical sets $E_1\cup E_2$ is replaced by $P_0+P_1-P_0P_1$ in the
case of quantum projection operators~\cite{Griffiths2003}, the last
condition, Eq.~(\ref{eq:QuantumInterval-valuedProbability-Inclusion}),
is a direct counterpart of Eq.~(\ref{eq:classicalconvex}). Thus the
definition of QIVPM is an amalgamation of both classical IVPMs and
conventional quantum probability measures.

In Sec.~\ref{sec:Gleason}, we will show that QIVPMs generalize
conventional quantum probability measures in the limit where the lower
and upper end of each interval coincide exactly. In the remainder of
this section, we will show that our definition of QIVPMs is consistent
with classical IVPMs in the sense that a restriction of QIVPMs to
commuting events recovers the definition of classical IVPMs.

\paragraph*{QIVPMs and Classical IVPMs.} To formalize this connection,
we first note that contrary to the case with conventional quantum
probability spaces, there is generally no unique state consistent with
a QIVPM. We say that a QIVPM $\bar{\mu}$ is consistent with a state
$\rho$ and projector $P$ if the interval $\bar{\mu}(P)$ contains the
exact probability calculated by the Born rule, i.e, if:
\begin{equation}
\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)
\end{equation}
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event~$P$ happens determined by the Born
rule~\citep{Born1983,peres1995quantum,544199}.

We generalize this consistency relation to sets of states and general
subspaces of events as follows. A set of events $\events'$ is a
\emph{subspace} if it contains $\mathbb{0}$ and $\mathbb{1}$ and is
closed under complements and sums, i.e., for any
projector~$P\in\events'$, we have $\mathbb{1}-P\in\events'$ and for
each pair of orthogonal projectors~$P_0 \in \events'$ and
$P_1 \in \events'$, we have $(P_0 + P_1) \in \events'$. Given a
probability measure $\bar{\mu}$ and a subspace of events $\events'$,
we can collect the set of all states $\coreBorn(\bar{\mu},\events')$
that are consistent with $\bar{\mu}$ on every projector in $\events'$
as:
\begin{equation}
\coreBorn\left(\bar{\mu},\events'\right)=\set{\textrm{state }\rho}{\forall P\in \events',~\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)}.
\end{equation}

In the long version of this paper, we establish that QIVPMs become
classical IVPMs when the space of events includes only mutually
commuting events. The idea of the proof is as follows. Given a
subspace of commuting events $\events_C$, we can construct a partial
orthonormal basis by diagonalization and complete it to a full
orthonornal basis $\overline{\events_C}$. We then build a bijection
between the QIVPM on the set of projectors associated with this basis
and the set of classical events corresponding to this basis. This
correspondence leads to a crucial property in our setting.

\begin{thm}\label{thm:Shapley}
  For a QIVPM~$\bar{\mu}:\events\rightarrow\mathscr{I}$, if a subspace
  of events~$\events'\subseteq\events$ commutes, then
  $\coreBorn\left(\bar{\mu},\events'\right)\ne\emptyset$.
\end{thm}

The theorem follows directly from our correspondence and Shapley's
theorem that proves that a classical IVPM always contains at least one
state that is consistent with every
event~\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016}. As we will
illustrate in the next section, the set of states
$\coreBorn\left(\bar{\mu},\events'\right)$ consistent with some events
$\events'$ and a particular QIVPM $\bar{\mu}$ may be
\emph{empty}.

For example, a well-defined  
QIVPM, assuming the three intervals $\imposs$, $\necess$, and
$\unknown=\left[0,1\right]$, is:
\begin{equation}
\bar{\mu}_{1}\left(P\right)=\begin{cases}
\imposs\,, & \text{if }P=\mathbb{0}\text{ ;}\\
\necess\,, & \text{if }P=\mathbb{1}\text{ ;}\\
\unknown\,, & \text{otherwise.}
\end{cases}\label{eq:no-information-IVPM}
\end{equation}
This measure represents the beliefs of an experimenter with no prior
knowledge about the particular quantum system in question; any quantum
state would be consistent with $\bar{\mu}_{1}$ on any projectors, and
$\coreBorn\left(\bar{\mu}_{1},\events\right)$ is just the set of all
states. The subspace
$\events_{0}=\left\{ \mathbb{0},\proj{0},\proj{1},\mathbb{1}\right\} $
is a subspace of commuting events. Indeed restricting $\bar{\mu}_{1}$
to $\events_{0}$, $\bar{\mu}_{1}|_{\events_{0}}$, gives a classical
IVPM~$\bar{\mu}_{2}$:
\begin{equation}
\begin{aligned}\bar{\mu}_{2}(\mathbb{0}) & =\imposs & \bar{\mu}_{2}(\proj{0}) & =\unknown\\
\bar{\mu}_{2}(\mathbb{1}) & =\necess & \bar{\mu}_{2}(\proj{1}) & =\unknown
\end{aligned}
\end{equation}
If we identify the states ~$\proj{0}$ and $\proj{1}$ with the head
and the tail of a coin, respectively, then $\bar{\mu}_{2}$ represents
the situation in which that an experimenter knows nothing about a coin
before she tosses it. Moreover, for each $p\in\left[0,1\right]$, the
state~$p\proj{0}+\left(1-p\right)\proj{1}$ represents a classical
coin with probability~$p$ to get heads, and
$p\proj{0}+\left(1-p\right)\proj{1}$ is consistent with
$\bar{\mu}_{2}$ on $\events_{0}$ because any classical coin should be
consistent with the situation for which an experimenter has no prior
knowledge.

@@

Our first result is that a QIVPM is consistent with the inability to avoid
uncertainty found in conventional infinite precise quantum
mechanics~\cite{PeresRon1988,peres1995quantum}.

\begin{thm}[Kochen-Specker~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}]\label{thm:Kochen-Specker}
  Given a Hilbert space $\Hilb$ of dimension~$d\ge3$, there is no
  0-deterministic
  measure~$\mu^{\mathrm{D}}:\events\rightarrow\left\{ 0,1\right\}
  $.\end{thm}
